Index measures for oak decline severity using phenotypic descriptors

### 2019-11-12 manuscript/supplementary.Rmd
supplementary now compiles

```{r descriptor_adjustment,fig.cap='Error bars show ±1SE of the mean.\nDashed red line shows the overall mean.'}
source('../code/descriptor_adjustment.R')
descriptor_adjustment %>%
  wrap_plots()
```

>>>>

---
output: pdf_document
---

```{r descriptor_adjustment,fig.cap='Error bars show ±1SE of the mean.\nDashed red line shows the overall mean.'}
loadd(descriptor_adjustment_example)

descriptor_adjustment_example %>%
  wrap_plots()
```
